---
title: "Machine_Learning_Peptide_Tax_Assign"
author: "ZhongzhiSun"
date: "2024-11-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath("../data/Drugs_dataset"))
```


---
title: "Applying Machine Learning Models to Peptide Abundance Data for Petpide Taxa Assignment"
author: "ZhongzhiSun"
date: "2024-09-18"
output: 
  html_document: default
  #pdf_document: default
  #word_document:
  #  reference_docx: docx_template.docx
---

Outline
==========

Studied family clusters: Burkholderiaceae, Eggerthellaceae, Bacteroidaceae...

Studied machine learning models: SVM, RandomForest(RF)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Read in peptide abundance correlation matrix
```{r, echo = FALSE, eval = TRUE}
library(dplyr)
library(data.table)
library(ComplexHeatmap)
library(circlize)
library(ggsci)
library(ggplot2)

individual <- "V52"

### Read in correlation matrix
correlation_matrix_file_name <- paste0(individual, "_fold_change_wide.out_SCC_correlation.wide.out")
correlation_matrix_file <- file.path("rm_mbr_individual_pep_scc", correlation_matrix_file_name)
readin_correlation_matrix <- fread(correlation_matrix_file, sep = "\t")
correlation_matrix <- as.matrix(readin_correlation_matrix[,-1])
rownames(correlation_matrix) <- readin_correlation_matrix$V1
nrow(correlation_matrix)

```


The abundance correlations between `r nrow(correlation_matrix)` peptides from the individual `r individual` were calculated.


### Readin peptide taxonomic annotations
```{r, echo = FALSE, eval = TRUE}
### Read in peptide taxonomic annotations
pep_prot_source_file_name <- paste0(individual, "_rm_mbr_quantified_peptides_refined_anno.out")
pep_prot_source_file <- file.path("rm_mbr_individual_pep_taxa_refine", pep_prot_source_file_name)
pep_prot_source <- read.table(pep_prot_source_file, header = TRUE, sep = "\t")
head(pep_prot_source, 5)


```


### Selecting peptides from specific family
```{r, echo = FALSE, eval = TRUE}
# "Bacteroidaceae" Family
# selected_family <- "Bacteroidaceae"
# GenomeA <- "MGYG000002281"
# GenomeB <- "MGYG000000243"

# "Enterobacteriaceae" Family
# selected_family <- "Enterobacteriaceae"
# GenomeA <- "MGYG000002506"
# GenomeB <- "MGYG000002494"

# "Lachnospiraceae" Family
# selected_family <- "Lachnospiraceae"
# GenomeA <- "MGYG000002528"
# GenomeB <- "MGYG000000212"

# "Eggerthellaceae" Family
# selected_family <- "Eggerthellaceae"
# GenomeA <- "MGYG000002544"
# GenomeB <- "MGYG000002487"

# "Burkholderiaceae" Family
selected_family <- "Burkholderiaceae"
GenomeA <- "MGYG000001294"
GenomeB <- "MGYG000003022"

### Selecting peptides from the specific family
# Define a filter to only keep genome with larger number of distinct peptides than the threshold
genome_pep_thresholds <- 10

# Get peptide list of selected family
selected_family_pep <- pep_prot_source %>% filter(Family == selected_family) %>% select("Peptide") %>% pull()
length(selected_family_pep)

selected_family_correlation_matrix <- correlation_matrix[rownames(correlation_matrix) %in% selected_family_pep, colnames(correlation_matrix) %in% selected_family_pep ]

# Statistics for the number of peptides from each genome
selected_pep_prot_source <- pep_prot_source %>% filter(Family == selected_family)
nrow(selected_pep_prot_source)

# Only keeping peptides from genomes with >= 10 distinct peptides
genome_pep_counts <- table(selected_pep_prot_source$Genome)
genomes_to_keep <- names(genome_pep_counts[genome_pep_counts >= genome_pep_thresholds])
selected_pep_prot_source <- selected_pep_prot_source %>% 
  filter(Genome %in% genomes_to_keep)
head(selected_pep_prot_source,5)

# Selecting these peptides from the matrix
selected_genome_pep <- selected_pep_prot_source %>% select("Peptide") %>% pull()
length(selected_genome_pep)
nrow(selected_family_correlation_matrix)
ncol(selected_family_correlation_matrix)
selected_genome_correlation_matrix <- selected_family_correlation_matrix[rownames(selected_family_correlation_matrix) %in% selected_genome_pep, colnames(selected_family_correlation_matrix) %in% selected_genome_pep]  


```


Currently, we are analyzing the family `r selected_family`.


### Extract training dataset
```{r, echo = FALSE, eval = TRUE}
selecting_percentage <- 0.7
### Randomly select 70% of peptides from each genome for training
set.seed(123)
# Extract training peptides from Genome A
GenomeA_all_pep <- selected_pep_prot_source %>% 
  filter(Genome == GenomeA) %>% 
  filter(Peptide %in% rownames(selected_family_correlation_matrix)) %>% 
  select("Peptide") %>% 
  pull()
train_size <- floor(selecting_percentage * length(GenomeA_all_pep))
GenomeA_train_pep <- sample(GenomeA_all_pep, size = train_size)
GenomeA_test_pep <- setdiff(GenomeA_all_pep, GenomeA_train_pep)

# Extract training peptides from Genome B
set.seed(123)
GenomeB_all_pep <- selected_pep_prot_source %>% 
  filter(Genome == GenomeB) %>% 
  filter(Peptide %in% rownames(selected_family_correlation_matrix)) %>% 
  select("Peptide") %>% 
  pull()
train_size <- floor(selecting_percentage * length(GenomeB_all_pep))
GenomeB_train_pep <- sample(GenomeB_all_pep, size = train_size)
GenomeB_test_pep <- setdiff(GenomeB_all_pep, GenomeB_train_pep)

### Prepare training data
all_train_pep <- c(GenomeA_train_pep, GenomeB_train_pep)
# Annotate training peptides
GenomeA_train_pep_anno <- data.frame(
  Peptide = GenomeA_train_pep,
  Genome = "GenomeA"
)
GenomeB_train_pep_anno <- data.frame(
  Peptide = GenomeB_train_pep,
  Genome = "GenomeB"
)
all_train_pep_anno <- rbind(GenomeA_train_pep_anno, GenomeB_train_pep_anno)
all_test_pep_anno <- rbind(GenomeA_test_pep, GenomeB_test_pep)

### Extract features for training and testing
train_features <- selected_family_correlation_matrix[all_train_pep, all_train_pep]
train_features_A <- selected_family_correlation_matrix[GenomeA_train_pep, all_train_pep]
train_features_B <- selected_family_correlation_matrix[GenomeB_train_pep, all_train_pep]

### Prepare final training dataset
train_features_df <- as.data.frame(train_features)
train_features_df$Peptide <- rownames(train_features_df)
train_data <- train_features_df %>%
  inner_join(all_train_pep_anno, by = "Peptide")
# Remove Peptide column and convert Genome to factor
train_data <- train_data %>% select(-Peptide)
train_data$Genome <- as.factor(train_data$Genome)
```



### Extract testing dataset.
```{r, echo = FALSE, eval = TRUE}
### Select test dataset 
# Testing dataset from GenomeA
GenomeA_test_pep <- setdiff(GenomeA_all_pep, GenomeA_train_pep)
# Testing dataset from GenomeB
GenomeB_test_pep <- setdiff(GenomeB_all_pep, GenomeB_train_pep)

test_features_A <- selected_family_correlation_matrix[GenomeA_test_pep, all_train_pep]
test_features_B <- selected_family_correlation_matrix[GenomeB_test_pep, all_train_pep]


### Select genome unannotated peptides
unannotated_pep <- selected_pep_prot_source %>% 
  filter(Genome == "-") %>% 
  filter(Peptide %in% rownames(selected_family_correlation_matrix)) %>% 
  select("Peptide") %>% 
  pull()
# Features of unannotated peptides
unannotated_features <- selected_family_correlation_matrix[unannotated_pep, all_train_pep]


### Select peptides annotated to other genomes from the same family
other_pep <- selected_pep_prot_source %>% 
  filter(Genome %in% genomes_to_keep) %>% 
  filter(Genome != "-" & Genome != GenomeA & Genome != GenomeB) %>% 
  filter(Peptide %in% rownames(selected_family_correlation_matrix)) %>% 
  select("Peptide") %>% 
  pull()
# Features of peptides annotated to other genomes
other_genomes_features <- selected_family_correlation_matrix[other_pep, all_train_pep]


### Select peptides annotated to other families
# Get all peptide row names from correlation matrix
all_peptides <- rownames(correlation_matrix)
# Get candidate peptides by removing selected family peptides
candidate_peptides <- setdiff(all_peptides, selected_family_pep)
# Randomly select 500 peptides not in selected family
set.seed(123)  # Set random seed for reproducibility
random_pep <- sample(candidate_peptides, 500)
# Extract testing features for peptides from other families
other_family_test_feature <- correlation_matrix[random_pep, all_train_pep]
```



### Training the SVM model.
```{r, echo = FALSE, eval = TRUE}
### Training Model
library(e1071)
model <- svm(Genome ~ ., data = train_data, kernel = "linear", probability = TRUE)
# Check the trained model
summary(model)

# Define cross-validation control parameters
# train_control <- trainControl(method="cv", number=5, classProbs=TRUE, summaryFunction=twoClassSummary)
# 
# Train model using random forest and calculate Cross Validation AUC
# model <- train(Genome ~ ., data=train_data, method="svmLinear", trControl=train_control, metric="ROC")
# 
# Print model cross-validation results, including AUC
# print(model)
```



### Evaluate the SVM model with peptides from other families
```{r, echo = FALSE, eval = TRUE}
### Combined Set1: Test set for Genome A and Genome B as well as peptides from other families
combined_other_fam_test_pep <- c(GenomeA_test_pep, GenomeB_test_pep, random_pep)
combined_other_fam_test_features <- correlation_matrix[combined_other_fam_test_pep, all_train_pep]
# Setting true labels
true_labels <- c(
  rep("GenomeA peptides", length(GenomeA_test_pep)),
  rep("GenomeB peptides", length(GenomeB_test_pep)),
  rep("Other peptides", length(random_pep))
)

# Evaluate for combined dataset with peptides from other families
pred_svm <- predict(model, as.data.frame(combined_other_fam_test_features), probability = TRUE)
pred_svm_prob <- attr(pred_svm, "probabilities")[, "GenomeA"]
# Assign labels based on probability
pred_labels_svm <- ifelse(
  pred_svm_prob >= 0.9, "GenomeA peptides",
  ifelse(pred_svm_prob <= 0.1, "GenomeB peptides", "Other peptides")
)

# Construct a dataframe for saving predict and real labels
results_df <- data.frame(
  Peptide = combined_other_fam_test_pep,
  TrueLabel = true_labels,
  PredictedLabel = pred_labels_svm,
  PredictedProbability = pred_svm_prob
)

# Setting levels and factors
levels <- c("GenomeA peptides", "GenomeB peptides", "Other peptides")
results_df$TrueLabel <- factor(results_df$TrueLabel, levels = levels)
results_df$PredictedLabel <- factor(results_df$PredictedLabel, levels = levels)

# 7. Calculate confusion matrix
library(caret)
conf_matrix <- confusionMatrix(results_df$PredictedLabel, results_df$TrueLabel)

# 8. View confusion matrix
print(conf_matrix$table)

# 9. Extract evaluation metrics for each class
metrics_by_class <- as.data.frame(conf_matrix$byClass)
metrics_by_class$Class <- rownames(metrics_by_class)

# 10. View Precision, Recall, Specificity for each class
print(metrics_by_class[, c("Class", "Precision", "Recall", "Specificity")])

# 11. Visualize results (optional)
library(ggplot2)

# Plot confusion matrix heatmap
conf_mat_df <- as.data.frame(conf_matrix$table)
ggplot(data = conf_mat_df, aes(x = Prediction, y = Reference, fill = Freq)) +
  geom_tile() +
  geom_text(aes(label = Freq), color = "white", size = 6) +
  scale_fill_gradient(low = "blue", high = "red") +
  labs(title = "Confusion Matrix for peptides from other families", x = "Predicted Label", y = "True Label", size = 6)
```


### Evaluate the SVM model with peptides from other genomes of the same family
```{r, echo = FALSE, eval = TRUE}
### Combined Set2: Test set for Genome A and Genome B as well as same number of peptides from other genomes
combined_same_fam_test_pep <- c(GenomeA_test_pep, GenomeB_test_pep, other_pep)
combined_same_fam_test_features <- correlation_matrix[combined_same_fam_test_pep, all_train_pep]

# Setting true labels
true_labels <- c(
  rep("GenomeA peptides", length(GenomeA_test_pep)),
  rep("GenomeB peptides", length(GenomeB_test_pep)),
  rep("Other peptides", length(other_pep))
)


pred_svm <- predict(model, as.data.frame(combined_same_fam_test_features), probability = TRUE)
pred_svm_prob <- attr(pred_svm, "probabilities")[, "GenomeA"]
# Assign labels based on probability
pred_labels_svm <- ifelse(
  pred_svm_prob >= 0.9, "GenomeA peptides",
  ifelse(pred_svm_prob <= 0.1, "GenomeB peptides", "Other peptides")
)

# Construct a dataframe for saving predict and real labels
results_df <- data.frame(
  Peptide = combined_same_fam_test_pep,
  TrueLabel = true_labels,
  PredictedLabel = pred_labels_svm,
  PredictedProbability = pred_svm_prob
)

# Setting levels and factors
levels <- c("GenomeA peptides", "GenomeB peptides", "Other peptides")
results_df$TrueLabel <- factor(results_df$TrueLabel, levels = levels)
results_df$PredictedLabel <- factor(results_df$PredictedLabel, levels = levels)

# 7. Calculate confusion matrix
library(caret)
conf_matrix <- confusionMatrix(results_df$PredictedLabel, results_df$TrueLabel)

# 8. View confusion matrix
print(conf_matrix$table)

# 9. Extract evaluation metrics for each class
metrics_by_class <- as.data.frame(conf_matrix$byClass)
metrics_by_class$Class <- rownames(metrics_by_class)

# 10. View Precision, Recall, Specificity for each class
print(metrics_by_class[, c("Class", "Precision", "Recall", "Specificity")])

# 11. Visualize results (optional)
library(ggplot2)

# Plot confusion matrix heatmap
conf_mat_df <- as.data.frame(conf_matrix$table)
ggplot(data = conf_mat_df, aes(x = Prediction, y = Reference, fill = Freq)) +
  geom_tile() +
  geom_text(aes(label = Freq), color = "white", size = 6) +
  scale_fill_gradient(low = "blue", high = "red") +
  labs(title = "Confusion Matrix for peptides from the same family", x = "Predicted Label", y = "True Label", size = 6)
```


### Applying SVM model to predict unannotated peptides.
```{r, echo = FALSE, eval = TRUE}
pred_svm <- predict(model, as.data.frame(unannotated_features), probability = TRUE)
pred_svm_prob <- attr(pred_svm, "probabilities")[, "GenomeA"]
# Assign labels based on probability
pred_labels_svm <- ifelse(
  pred_svm_prob >= 0.9, "GenomeA peptides",
  ifelse(pred_svm_prob <= 0.1, "GenomeB peptides", "Other peptides")
)


# Construct a dataframe for saving predict and real labels
results_df <- data.frame(
  Peptide = unannotated_pep,
  PredictedLabel = pred_labels_svm,
  PredictedProbability = pred_svm_prob
)

table(results_df$PredictedLabel)

# Plot the score distribution
ggplot(results_df, aes(x = PredictedProbability)) +
  geom_histogram(fill = "#FFBB78FF", position = "identity", bins = 40, alpha = 0.5) +
  labs(title = "Histogram of Prediction Probabilities", x = "Prediction Probability", y = "Count") +
  theme_bw() +
  scale_x_continuous(limits = c(-0.03, 1.03), breaks = seq(0, 1, by = 0.1), expand = expansion(mult = c(0, 0))) +
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.1))) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 18),
    axis.title.x = element_text(size = 14, color = "black"),
    axis.title.y = element_text(size = 14, color = "black"),
    axis.text.x = element_text(size = 12, color = "black"),
    axis.text.y = element_text(size = 12, color = "black"),
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    plot.margin = ggplot2::margin(t = 0, r = 15, b = 0, l = 0, unit = "pt")
  )

```



### Training the Random Forest (RF) model.
```{r, echo = FALSE, eval = TRUE}
### Training the Random Forest model
library(randomForest)
model <- randomForest(Genome ~ ., data = train_data, ntree = 500, importance = TRUE)

# Check the trained model
summary(model)
```



### Evaluate the Random Forest (RF) model with peptides from the test dataset.
```{r}
### Evaluate the prediction with test dataset
# Predict on test set
pred_A_value <- predict(model, as.data.frame(test_features_A), type = "prob")
pred_B_value <- predict(model, as.data.frame(test_features_B), type = "prob")


pred_A_value_df <- as.data.frame(pred_A_value)
pred_A_value_df$Peptide <- rownames(pred_A_value)
pred_A_value_df$Genome <- "GenomeA"

pred_B_value_df <- as.data.frame(pred_B_value)
pred_B_value_df$Peptide <- rownames(pred_B_value)
pred_B_value_df$Genome <- "GenomeB"

pred_values_df <- rbind(pred_A_value_df, pred_B_value_df)


# Histogram plot
myplot <- ggplot(pred_values_df, aes(x = GenomeA, fill = Genome)) +
  geom_histogram(position = "identity", bins = 40, alpha = 0.5) +
  labs(title = "Genome-distinct Peptides in the Testing Dataset", x = "Predicted probability of peptides sourcing from Genome A", y = "Number of peptides") +
  scale_fill_manual(values = c("GenomeA" = "#D62728FF", "GenomeB" = "#1F77B4FF")) +
  theme_bw() +
  scale_x_continuous(limits = c(-0.03, 1.03), breaks = seq(0, 1, by = 0.1), expand = expansion(mult = c(0, 0))) +
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.1))) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 18),
    axis.title.x = element_text(size = 14, color = "black"),
    axis.title.y = element_text(size = 14, color = "black"),
    axis.text.x = element_text(size = 12, color = "black"),
    axis.text.y = element_text(size = 12, color = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    plot.margin = ggplot2::margin(t = 0, r = 15, b = 0, l = 0, unit = "pt")
  )
myplot
```





### Evaluate the Random Forest (RF) model with peptides from other families.
```{r, echo = FALSE, eval = TRUE}
### Prediction probabilities of peptides from other families
other_fam_test_pep <- c(random_pep)
other_fam_test_features <- correlation_matrix[other_fam_test_pep, all_train_pep]

# Predict and get probabilities for GenomeA
pred_rf_prob <- predict(model, as.data.frame(other_fam_test_features), type = "prob")[, "GenomeA"]

# Construct a dataframe for saving prediction probabilities
results_df <- data.frame(
  Peptide = other_fam_test_pep,
  PredictedProbability = pred_rf_prob
)

table(results_df$PredictedLabel)

# Statistics for the number of peptides assigned neither to Genome A nor to Genome B
filtered_results_df <- results_df %>% filter(PredictedProbability > 0.1 & PredictedProbability < 0.9)
nrow(filtered_results_df)
nrow(filtered_results_df)/length(other_fam_test_pep)

# Plot the score distribution
ggplot(results_df, aes(x = PredictedProbability)) +
  geom_histogram(fill = "#F4A261", position = "identity", bins = 40, alpha = 0.5) +
  labs(title = "Peptides from Other Families", x = "Predicted probability of peptides sourcing from Genome A", y = "Number of peptides") +
  theme_bw() +
  scale_x_continuous(limits = c(-0.03, 1.03), breaks = seq(0, 1, by = 0.1), expand = expansion(mult = c(0, 0))) +
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.1))) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 18),
    axis.title.x = element_text(size = 14, color = "black"),
    axis.title.y = element_text(size = 14, color = "black"),
    axis.text.x = element_text(size = 12, color = "black"),
    axis.text.y = element_text(size = 12, color = "black"),
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    plot.margin = ggplot2::margin(t = 0, r = 15, b = 0, l = 0, unit = "pt")
  )



### Confusion Matrix of Combined Set1: Test set for Genome A and Genome B as well as peptides from other families
# Random Forest Model
# Predict and get probabilities for test set
combined_other_fam_test_pep <- c(GenomeA_test_pep, GenomeB_test_pep, random_pep)
combined_other_fam_test_features <- correlation_matrix[combined_other_fam_test_pep, all_train_pep]
pred_rf_prob <- predict(model, as.data.frame(combined_other_fam_test_features), type = "prob")[, "GenomeA"]

# Predict and get probabilities for test set
pred_rf_prob <- predict(model, as.data.frame(combined_other_fam_test_features), type = "prob")[, "GenomeA"]

# Assign labels based on probability
pred_labels_rf <- ifelse(
  pred_rf_prob >= 0.9, "GenomeA peptides",
  ifelse(pred_rf_prob <= 0.1, "GenomeB peptides", "Other peptides")
)

# Setting true labels
true_labels <- c(
  rep("GenomeA peptides", length(GenomeA_test_pep)),
  rep("GenomeB peptides", length(GenomeB_test_pep)),
  rep("Other peptides", length(random_pep))
)


# Construct a dataframe for saving predict and real labels
results_df <- data.frame(
  Peptide = combined_other_fam_test_pep,
  TrueLabel = true_labels,
  PredictedLabel <- pred_labels_rf,
  PredictedProbability = pred_rf_prob
)


# Setting levels and factors
levels <- c("GenomeA peptides", "GenomeB peptides", "Other peptides")
results_df$TrueLabel <- factor(results_df$TrueLabel, levels = levels)
results_df$PredictedLabel <- factor(results_df$PredictedLabel, levels = levels)


# 7. Calculate confusion matrix
library(caret)
conf_matrix <- confusionMatrix(results_df$PredictedLabel, results_df$TrueLabel)

# 8. View confusion matrix
print(conf_matrix$table)

# 9. Extract evaluation metrics for each class
metrics_by_class <- as.data.frame(conf_matrix$byClass)
metrics_by_class$Class <- rownames(metrics_by_class)

# 10. View Precision, Recall, Specificity for each class
print(metrics_by_class[, c("Class", "Precision", "Recall", "Specificity")])

# 11. Visualize results (optional)
library(ggplot2)

# Plot confusion matrix heatmap
conf_mat_df <- as.data.frame(conf_matrix$table)
# ggplot(data = conf_mat_df, aes(x = Prediction, y = Reference, fill = Freq)) +
#   geom_tile() +
#   geom_text(aes(label = Freq), color = "white", size = 6) +
#   scale_fill_gradient(low = "blue", high = "red") +
#   labs(title = "Confusion Matrix for peptides from the other families", x = "Predicted Label", y = "True Label")

ggplot(data = conf_mat_df, aes(x = Prediction, y = Reference, fill = Freq)) +
  geom_tile() +
  geom_text(aes(label = Freq), color = "white", size = 6, fontface = "bold") +
  scale_fill_viridis_c(option = "viridis", direction = 1) +
  labs(title = "Confusion Matrix for Peptides from Other Families", 
       x = "Predicted Label", 
       y = "True Label", 
       fill = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title.x = element_text(size = 16, color = "black"),
    axis.title.y = element_text(size = 16, color = "black"),
    axis.text.x = element_text(size = 12,  color = "black"),
    axis.text.y = element_text(size = 12, color = "black"),
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    legend.position = "none"            # Set legend position to none
  )

```



### Evaluate the Random Forest (RF) model with peptides from other genomes of the same family.
```{r, echo = FALSE, eval = TRUE}
### Prediction probabilities of peptides from other families
same_fam_test_pep <- c(other_pep)
same_fam_test_features <- correlation_matrix[same_fam_test_pep, all_train_pep]

# Predict and get probabilities for GenomeA
pred_rf_prob <- predict(model, as.data.frame(same_fam_test_features), type = "prob")[, "GenomeA"]

# Construct a dataframe for saving prediction probabilities
results_df <- data.frame(
  Peptide = same_fam_test_pep,
  PredictedProbability = pred_rf_prob
)

table(results_df$PredictedLabel)

# Statistics for the number of peptides assigned neither to Genome A nor to Genome B
filtered_results_df <- results_df %>% filter(PredictedProbability > 0.1 & PredictedProbability < 0.9)
nrow(filtered_results_df)
nrow(filtered_results_df)/length(same_fam_test_pep)

# Plot the score distribution
ggplot(results_df, aes(x = PredictedProbability)) +
  geom_histogram(fill = "#F4A261", position = "identity", bins = 40, alpha = 0.5) +
  labs(title = "Peptides from Other Genomes of the same Family", x = "Predicted probability of peptides sourcing from Genome A", y = "Number of peptides") +
  theme_bw() +
  scale_x_continuous(limits = c(-0.03, 1.03), breaks = seq(0, 1, by = 0.1), expand = expansion(mult = c(0, 0))) +
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.1))) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 18),
    axis.title.x = element_text(size = 14, color = "black"),
    axis.title.y = element_text(size = 14, color = "black"),
    axis.text.x = element_text(size = 12, color = "black"),
    axis.text.y = element_text(size = 12, color = "black"),
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    plot.margin = ggplot2::margin(t = 0, r = 15, b = 0, l = 0, unit = "pt")
  )



### Combined Set1: Test set for Genome A and Genome B as well as peptides from other genomes of the same family
# Random Forest Model
# Predict and get probabilities for test set
pred_rf_prob <- predict(model, as.data.frame(combined_same_fam_test_features), type = "prob")[, "GenomeA"]

# Assign labels based on probability
pred_labels_rf <- ifelse(
  pred_rf_prob >= 0.9, "GenomeA peptides",
  ifelse(pred_rf_prob <= 0.1, "GenomeB peptides", "Other peptides")
)

# Setting true labels
true_labels <- c(
  rep("GenomeA peptides", length(GenomeA_test_pep)),
  rep("GenomeB peptides", length(GenomeB_test_pep)),
  rep("Other peptides", length(other_pep))
)


# Construct a dataframe for saving predict and real labels
results_df <- data.frame(
  Peptide = combined_same_fam_test_pep,
  TrueLabel = true_labels,
  PredictedLabel <- pred_labels_rf,
  PredictedProbability = pred_rf_prob
)


# Setting levels and factors
levels <- c("GenomeA peptides", "GenomeB peptides", "Other peptides")
results_df$TrueLabel <- factor(results_df$TrueLabel, levels = levels)
results_df$PredictedLabel <- factor(results_df$PredictedLabel, levels = levels)


# 7. Calculate confusion matrix
library(caret)
conf_matrix <- confusionMatrix(results_df$PredictedLabel, results_df$TrueLabel)

# 8. View confusion matrix
print(conf_matrix$table)

# 9. Extract evaluation metrics for each class
metrics_by_class <- as.data.frame(conf_matrix$byClass)
metrics_by_class$Class <- rownames(metrics_by_class)

# 10. View Precision, Recall, Specificity for each class
print(metrics_by_class[, c("Class", "Precision", "Recall", "Specificity")])

# 11. Visualize results (optional)
library(ggplot2)

# Plot confusion matrix heatmap
conf_mat_df <- as.data.frame(conf_matrix$table)
# ggplot(data = conf_mat_df, aes(x = Prediction, y = Reference, fill = Freq)) +
#   geom_tile() +
#   geom_text(aes(label = Freq), color = "white", size = 6) +
#   scale_fill_gradient(low = "blue", high = "red") +
#   labs(title = "Confusion Matrix for peptides from the same family", x = "Predicted Label", y = "True Label")

ggplot(data = conf_mat_df, aes(x = Prediction, y = Reference, fill = Freq)) +
  geom_tile() +
  geom_text(aes(label = Freq), color = "white", size = 6, fontface = "bold") +
  scale_fill_viridis_c(option = "viridis", direction = 1) +
  labs(title = "Confusion Matrix for Peptides from the Same Family", 
       x = "Predicted Label", 
       y = "True Label", 
       fill = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title.x = element_text(size = 16, color = "black"),
    axis.title.y = element_text(size = 16, color = "black"),
    axis.text.x = element_text(size = 12,  color = "black"),
    axis.text.y = element_text(size = 12, color = "black"),
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    legend.position = "none"            
  )
```


### Applying Random Forest (RF) model to predict unannotated peptides.
```{r, echo = FALSE, eval = TRUE}
# # Random Forest Model
# Predict and get probabilities for test set
pred_rf_prob <- predict(model, as.data.frame(unannotated_features), type = "prob")[, "GenomeA"]

# Assign labels based on probability
pred_labels_rf <- ifelse(
  pred_rf_prob >= 0.9, "GenomeA peptides",
  ifelse(pred_rf_prob <= 0.1, "GenomeB peptides", "Other peptides")
)


# Construct a dataframe for saving predict and real labels
results_df <- data.frame(
  Peptide = unannotated_pep,
  PredictedLabel = pred_labels_rf,
  PredictedProbability = pred_rf_prob
)

table(results_df$PredictedLabel)

# Statistics for the number of peptides assigned neither to Genome A nor to Genome B
filtered_results_df <- results_df %>% filter(PredictedProbability > 0.1 & PredictedProbability < 0.9)
nrow(filtered_results_df)
1-nrow(filtered_results_df)/nrow(unannotated_features)

# Plot the score distribution
ggplot(results_df, aes(x = PredictedProbability)) +
  geom_histogram(fill = "#F4A261", position = "identity", bins = 40, alpha = 0.5) +
  labs(title = "Peptides without Genome-level annotation in the Family", x = "Predicted probability of peptides sourcing from Genome A", y = "Number of peptides") +
  theme_bw() +
  scale_x_continuous(limits = c(-0.03, 1.03), breaks = seq(0, 1, by = 0.1), expand = expansion(mult = c(0, 0))) +
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.1))) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 18),
    axis.title.x = element_text(size = 14, color = "black"),
    axis.title.y = element_text(size = 14, color = "black"),
    axis.text.x = element_text(size = 12, color = "black"),
    axis.text.y = element_text(size = 12, color = "black"),
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    plot.margin = ggplot2::margin(t = 0, r = 15, b = 0, l = 0, unit = "pt")
  )
```